### 2014-11-16 paper_dec/paper_dec.tex
update gitignore
Sneuvelversie MongoDB af

>>>>

\section{Document stores}

\subsection{MongoDB}

MongoDB stores data in .BSON (binary JSON) documents. It has powerful indexing support, with the ability to define secondary indexes of a wide array of types on all attributes, much like in the traditional relational model \cite{mongodb_indexes}. To aid with denormalization, the documents can contain embedded documents and arrays, thus obviating the need for joins in the query language.
\\MongoDB offers API's in many languages and the functionality to define the equivalent of SQL WHERE-clauses as javascript expressions. These are then translated to MongoDB's proprietary internal querying language \cite{grolinger2013data}. The MongoDB query optimizer processes queries and chooses the most efficient query plan for a query given the available indexes. These plans are cached if there are multiple viable options, and can be reevaluated as the data evolves \cite{mongodb_query_plans}.
\\The consistency of MongoDB is configurable, strong consistency can be attained in two ways: setting the connection to read-only from the master node (which has the most up-to-date version of the data), or forcing a write to succeed only after all replicas have acknowledged it. The former degrades the scaling ability of read requests, the later the latency of write requests \cite{grolinger2013data}.
For concurrency control, MongoDB offers single-document atomicity and implements reader-writer locks. Having to lock on writes severely impacts performance in write-intensive scenarios.
\\\\As a wrap-up, MongoDB stores BSON-files accessible through many API's with flexible querying and indexing techniques, but its concurrency and consistency model have some drawbacks.

\subsection{CouchBase Server}
